\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-05 fully-abstract-comp/popl2019/paper.tex
Minor textual changes to StkTokens section.

Our \stktokens{} calling convention is based on a traditional single stack, shared between all components.
As we are on a capability machine, it is natural to add some extra protection to stack and return pointers.
First, we replace stack pointers with stack capabilities.
When a new stack frame is created, the caller provisions it with a stack capability, restricted to the appropriate range, i.e.\ it does not cover the caller's stack frame.
Return pointers, on the other hand, are replaced by a pair of sealed return capabilities.
% KJAA: Again with the sealed pair. Again, this idea is unclear.
They form an opaque closure that the callee can only jump to, and the caller's data becomes available to the caller's return code.

%informally explain how an adversary may try to abuse stack and return caps
While the above adds extra protection, it is important to understand that it is not sufficient for enforcing WBCF and LSE.
While adversaries only get access to capabilities that they are allowed to use during the stack frame, they have ways to store these capabilities and use them when they are no longer allowed to do so.
Figure~\ref{fig:stack-ret-ptr-abuse} illustrates two examples of this.
In both examples our component and some adversarial component have been taking turns calling each other, so the stack now contains four stack frames alternating between ours and theirs.
The figure on the left (Figure~\ref{fig:stack-ptr-abuse}) illustrates how we try to ensure LSE by restricting the stack capability to the unused part before every call to the adversary.
However, restricting the stack capability does not help when we in the first call give access to the part of the stack where our second stack frame will reside as nothing prevents the adversary from duplicating and storing the stack pointer.
Generally speaking, we have no reason to ever trust a stack capability received from a component we do not trust as that stack capability may have been duplicated and stored for later use.
In the figure on the right (Figure~\ref{fig:ret-ptr-abuse}), we have given the adversary two pairs of sealed return capabilities, one in each of the two calls to the adversarial component.
The adversary may have stored the pair of sealed return capabilities from the first call in order to use it in the second call where they are not allowed to use it.
The figure illustrates how the adversarial code uses the return pair from the first call to return from the second call and thus break WBCF.

\todo[inline]{If target cap. machine is introduced before this section, then revisit/delete this section.}
% Informally explain how we prevent this using linear capabilities
As the examples illustrate, the standard memory and object-like capabilities (sealed capabilities) do not provide sufficient guarantees to enforce LSE and WBCF.
The two properties can be enforced with a calling convention that utilizes the guarantees of linear capabilities.

>>>>

\stktokens{} is based on a traditional single stack, shared between all components.
As we are on a capability machine, it is natural to add some extra protection to stack and return pointers.
First, we replace stack pointers with stack capabilities.
When a new stack frame is created, the caller provisions it with a stack capability, restricted to the appropriate range, i.e.\ it does not cover the caller's stack frame.
Return pointers, on the other hand, are replaced by a pair of sealed return capabilities.
% KJAA: Again with the sealed pair. Again, this idea is unclear.
They form an opaque closure that the callee can only jump to, and the caller's data becomes available to the caller's return code.

%informally explain how an adversary may try to abuse stack and return caps
While the above adds extra protection, it is not sufficient to enforce WBCF and LSE.
The caller provides the adversary with a stack capability and a return pair that they are supposed to use for the call, but the adversary can store the provided capabilities on the heap in order to use them later.
Figure~\ref{fig:stack-ret-ptr-abuse} illustrates two examples of this.
In both examples our component and some adversarial component have been taking turns calling each other, so the stack now contains four stack frames alternating between ours and theirs.
The figure on the left (Figure~\ref{fig:stack-ptr-abuse}) illustrates how we try to ensure LSE by restricting the stack capability to the unused part before every call to the adversary.
However, restricting the stack capability does not help when we in the first call give access to the part of the stack where our second stack frame will reside as nothing prevents the adversary from duplicating and storing the stack pointer.
Generally speaking, we have no reason to ever trust a stack capability received from a component we do not trust as that stack capability may have been duplicated and stored for later use.
In the figure on the right (Figure~\ref{fig:ret-ptr-abuse}), we have given the adversary two pairs of sealed return capabilities, one in each of the two calls to the adversarial component.
The adversary may have stored the pair of sealed return capabilities from the first call in order to use it in the second call where they are not allowed to use it.
The figure illustrates how the adversarial code uses the return pair from the first call to return from the second call and thus break WBCF.

\todo[inline]{If target cap. machine is introduced before this section, then revisit/delete this section.}
% Informally explain how we prevent this using linear capabilities
As the examples illustrate, the standard memory and object-like capabilities (sealed capabilities) do not provide sufficient guarantees to enforce LSE and WBCF.
The two properties can, however, be enforced with a calling convention that utilizes the guarantees of linear capabilities.
